Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2017-01-17 jssst/paper.tex
Final version (最終原稿)

\begin{table}[t]
    \centering
\caption{Development procedure of existing and proposed frameworks}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c}
                            & Development procedure \\ \hline
        Exisiting framework &    (1) + (2) + (3)    \\ %\hline
        Proposed framework  &          (4)          \\ \hline
        \multicolumn{2}{l}{ (1): Rewrite the storage device} \\
        \multicolumn{2}{l}{ (2): Insert the storage device into the target} \\
        \multicolumn{2}{l}{ (3): Restart the RTOS on the target (about 4 sec)} \\
        \multicolumn{2}{l}{ (4): Transfer an mruby bytecode from host to target} \\
    \end{tabular}
    }
    \label{tab:procedure}
\end{table}

@@

%\subsubsection{Code size utilizing component-based development}
To demonstrate the superiority of CBD, a comparison of the number of lines of codes C and ACL codes between two situations is shown in Table \ref{tab:codesize}.
In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Fig. \ref{fig:Eventflag}, respectively. 
For C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVMs increases.
Note that (B)'s C file can be utilized without modification regardless of the number of RiteVMs.
Moreover, the number of code lines of two CDL files are equal.
Skillful CBD yields advantages such as the decreased number of lines of codes and non-modified codes, which facilitates high productivity and maintainability.

@@

In the future, CDL files for the RiteVM and mruby-TECS bridge will be generated automatically using a plugin, and developers will be able to transfer bytecodes using the ZMODEM protocol on the command line.
Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.

%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgement}

This work was supported by JSPS KAKENHI Grant Number 15H05305.
We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.

%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrv}
\bibliography{ref}

>>>>

\begin{table}[t]
    \centering
\caption{Development procedure of existing and proposed frameworks}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c}
                            & Development procedure \\ \hline
        Existiting framework &    (1) + (2) + (3)    \\ %\hline
        Proposed framework  &          (4)          \\ \hline
        \multicolumn{2}{l}{ (1): Rewrite the storage device} \\
        \multicolumn{2}{l}{ (2): Insert the storage device into the target} \\
        \multicolumn{2}{l}{ (3): Restart the RTOS on the target (about 4 sec)} \\
        \multicolumn{2}{l}{ (4): Transfer an mruby bytecode from host to target} \\
    \end{tabular}
    }
    \label{tab:procedure}
\end{table}

@@

%\subsubsection{Code size utilizing component-based development}
To demonstrate the superiority of CBD, a comparison of the number of lines of C and CDL codes between two situations is shown in Table \ref{tab:codesize}.
In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Fig. \ref{fig:Eventflag}, respectively. 
For C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVMs increases.
Note that (B)'s C file can be utilized without modification regardless of the number of RiteVMs.
Moreover, the number of code lines of two CDL files are equal.
Skillful CBD yields advantages such as the decreased number of lines of codes and non-modified codes, which facilitates high productivity and maintainability.

@@

In the future, CDL files for the RiteVM and mruby-TECS bridge will be generated automatically using a plugin, and developers will be able to transfer bytecodes using the ZMODEM protocol on the command line.
Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.\newline

%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Acknowledgement}
{\bf Acknowledgement}\ 
This work was supported by JSPS KAKENHI Grant Number 15H05305.
We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.

%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{article/jssst}
\bibliography{ref}

### 2017-01-17 jssst/reply_letter.tex
Final version (最終原稿)

% cover letter
\begin{flushleft}
  2017-01-13\newline 
  ソフトウェア論文特集\newline
  論文・記事番号：16-S-05\newline
  題目：Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development\newline
  著者: Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi\newline
\end{flushleft}
\textbf{Dear Editor and Reviewer,}\newline

We highly appreciate the insightful suggestions and detailed valuable comments on our paper. 
The suggestions of the reviewers are very helpful for us and the suggestions are now incorporated in the revised paper as follows.
We have attached the last paper review and revised paper in our reply letter.
We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.\newline\newline

@@

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your suggestion.
We have added and modified the section as follows. (page 13)

@@

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your careful reading.
We have modified other contributions to ``:'' such as "Improved software development efficiency:". (page 3)
  \end{flushleft}

@@

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your suggestion.
As you said, we used the different figure.
We have replaced it with the correct figure. (page 7)
  \end{flushleft}

@@

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your suggestion.
We have switched the order of Fig. 12 and Fig. 13. (page 7-8)
  \end{flushleft}

>>>>

% cover letter
\begin{flushleft}
  2017-01-13\newline 
  ソフトウェア論文特集\newline
  論文・記事番号：16-S-05\newline
  題目：Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development\newline
  著者: Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi\newline
\end{flushleft}

\textbf{Dear Editor and Reviewer,}\newline

We highly appreciate the insightful suggestions and detailed valuable comments on our paper.
The suggestions of the reviewers are very helpful for us and the suggestions are now incorporated in the revised paper as follows.
We have attached the last paper review and revised paper in our reply letter.
In the revised paper, newly added and modified sentences are written in the bold and red colored font so that the reviewers can easily find them.
We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.
\newline\newline

@@

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your thoughtful suggestion.
We have added and modified the section as follows. (page 13)

@@

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for pointing out the wrong expression.
We have modified the other contributions to ``:'' such as "Improved software development efficiency:". (page 3)
  \end{flushleft}

@@

  \begin{flushleft}
    \textbf{Our reply:}
Thank you very much for your careful reading.
As you said, we used the different figure.
We have replaced it with the correct figure. (page 7)
  \end{flushleft}

@@

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your thoughtful comment.
We have switched the order of Fig. 12 and Fig. 13. (page 7-8)
  \end{flushleft}
